
\begin{frame}{Verifiable Computation}
	
		% what it is \begin{frame}{Motivation: Outsourcing Computation}
		\begin{block}{The Context}
			A \textit{delegator} requests a \textit{worker} to compute a function $f$ on input $x$.
		\end{block}
		\onslide<+->
		\begin{itemize}[<+- | alert@+>]
			\item Large scale distributed computation (e.g. volunteer computation, SETI@home,\dots)
			\item Cloud computing.
			\item Weak peripheral devices.
		\end{itemize}
		
		\onslide<+->
		\center{\Large{\textbf{The Main Problem of Verifiable Computation:}}\\
			\onslide<+-> \large{Building protocols to handle untrusted workers.}}

		% Motivation	
\end{frame}
%
\begin{frame}{Rational Model}
	\begin{block}{Assumption: }
		Workers have incentives and will act to maximize their utility.
	\end{block}
	\pause
\begin{block}{Incentives in Outsourced Computation:}
	\begin{itemize}[<+- | alert@+>]
		\item \textbf{e.g.} payments for computations on the cloud; % XXX: who applies this model?
		\item \textbf{e.g.} 'rewarded' volunteer computation (e.g. SETI@HOME and GridCoin);
		\item \textbf{e.g.} reward for mining in cryptocurrencies.
	\end{itemize}
\end{block}
\onslide<+->
\begin{block}{Abstracting incentives:}
\begin{itemize}[<+- | alert@+>]
	\item utility $ = $  payment (\textit{reward}) the worker gets;
	\small{
		\begin{itemize}
			\item (More realistically) utility $ = $ reward $ - $ cost (\textit{profit}).
			\item But we will temporarily ignore costs.
		\end{itemize}}
	\end{itemize}
\end{block}
\end{frame}


\begin{frame}{Approach: ``Correct Result $\iff$ Highest Pay'' [BCEJKL08]}
	\onslide<+->
	\begin{block}{\Large{To achieve}}
		\center{\Large{protocols ``secure'' against rational adversaries...}}
	\end{block}
	
	\medskip
	\pause
	\begin{block}{\Large{we  make sure that}}
		\center{\Large{we pay less for an incorrect result.}}
% \pause \Large{\textbf{$\Leftarrow$ New goal.}}}
	\end{block}
	\pause
	\alert{(All this, in expectation)}.
	
\end{frame}

\begin{frame}{Design Goals in This work}
\begin{itemize}[<+- | alert@+>]
	\item Efficiency (especially for verification);
	\item Minimal (or no) complexity assumptions.
\end{itemize}
\end{frame}

\begin{frame}{This Proposal: A Roadmap}
	\begin{enumerate}[<+- | alert@+>]
		\item An overview of rational proofs [AM12];
		\item Our results:
		\begin{enumerate}
			\item A critique of rational proofs: delegating multiple inputs; [\textbf{C}G15]
			\item Protocols for delegating space-bounded computations; [\textbf{C}G17]
		\end{enumerate}
		\item Results in progress: alternative approaches to rational proofs.
		\item Comparison, further applications, open problems.
	\end{enumerate}
\end{frame}

