\section{Introduction}

\begin{frame}{Motivation}

\begin{columns}
	\begin{column}{0.67\textwidth}
\begin{block}{The Context}
	A \textit{delegator} requests a \textit{worker} to perform a computation for her.
\end{block}
\onslide<+->
\begin{itemize}[<+- | alert@+>]
	\item Large scale distributed computation (e.g. volunteer computation, SETI@home,\dots)
	\item Cloud computing.
	\item Weak peripheral devices.
\end{itemize}
\end{column}
\begin{column}{0.33\textwidth}
[Picture here]
\end{column}
\end{columns}
\pause
\bigskip
\textbf{Goal of Verifiable Computation (VC):} \textit{Verifying} the work of \textit{untrusted} workers.
\end{frame}

\begin{frame}{Rational Verifiable Computation}
\textbf{Goal of Verifiable Computation (VC):} \textit{Verifying} the work of \textit{untrusted} workers.\pause

\textbf{Our Focus: } VC where workers are \textbf{rational}, \pause i.e. maximizing \textit{incentives}. \pause

\bigskip
\textbf{Is this model plausible?}

%TODO: add context for rational provers
% TODO: Add picture 

\end{frame}

\begin{frame}{Is this Model a Plausible Approximation?}
\begin{block}{Incentives in Outsourced Computation:}
	\begin{itemize}[<+- | alert@+>]
		\item  payments for computations on the cloud; % XXX: who applies this model?
		\item 'rewarded' volunteer computation (SETI\@ HOME, GridCoin);
		\item  rewards for mining in cryptocurrencies.
	\end{itemize}
\end{block}\pause 
\textbf{What are the Advantages?}
\end{frame}

\begin{frame}{Advantages of Exploiting Rationality}

	\begin{itemize}[<+- | alert@+>]
		\item Efficient Protocols (especially verification);
		\item Simple Protocols;
		\item  Unconditional Results (often).
	\end{itemize}

\end{frame}

% Metaphor

% TODO: Add next to each point a hint about the parts of the talk related to it.
\begin{frame}{My Thesis, Succinctly}
	\begin{enumerate}
		\item We can efficiently delegate (subsets of) \textit{feasible} computations to a rational server.\pause
		\item If a server ``cares'' about \textit{costs of computation}, existing techniques won't work when delegating multiple times; \pause I describe techniques without this flaw.\pause
		\item As an alternative approach to solve (2), with minimal assumptions we can design protocols where \textit{cheating does cost more} than acting honestly.
	\end{enumerate}
\end{frame}

% Papers
\begin{frame}{Papers Related to This Thesis}
\begin{itemize}
	\item M. Campanelli, and R. Gennaro. ``Sequentially composable rational proofs." \textit{International Conference on Decision and Game Theory for Security. Springer, Cham, 2015.}
	\item M. Campanelli, and R. Gennaro. ``Efficient Rational Proofs for Space Bounded Computations." \textit{International Conference on Decision and Game Theory for Security. Springer, Cham, 2017.}
	\item M. Campanelli and R. Gennaro. ``Fine-Grained Secure Computation'' \textit{Submitted to TCC 2018}
\end{itemize}
\end{frame}


